---
title: "Assignment"
description: |
  A short description of the post.
author:
  - name: Li Zhenglong
    url: {}
date: 03-28-2021
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    self_contained: false,
    code_folding:  TRUE
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "##",
  R.options = list(width = 60)
 
)


```


## 1.0 Overview

### 1.1 Objective

The study objective is to seek insight from Prime Mover (PM) Operations from port operations to identify common characteristics exhibited by PM with high and low waiting times, through understanding of PM events and operational data. This, in turn, enables us to pinpoint and identify correlated attributes and embark on further study to improve the overall productivity of PM operations and resource utilisation through active targeting of activities contributing to the PM waiting time.

### 1.2 Literature review

Current studies of PM productivity focus much on waiting time majoring of the operation time were spent. effort in improving resource planning yard storage and berth planning. 

Current operation performances are tracked using Operation Indicators such as PM productivity and PM waiting time aggregated by duration, from shifts to monthly reports and breakdown by individual terminal and PM.

Previous studies on PM operation efficiency typically focus on crane productivity by work schedule , and resource planning & deployment to find the optimal number of PMs and trucks (haulier) to reduce average PM waiting time.



### 1.3 Components of Data Visualisation

Pareto diagrams and control charts are used together to help tunnel down into the process to find the root cause of problems
The delivery data are examined using a control chart to determine if the problem is special causes of variation or just common causes of variation. The Pareto diagram is then used to determine the major reason for delivery problems.

The types of data visualizations used, and corresponding rationales are listed below:
    1. Pareto Chart
    
    2. Control chart

### 1.4 Sketch of Proposed Visualisation
### 1.5 Interactivity

The following interactive features are proposed to be incorporated in the data visualisations to enhance usability and hence user experience: 
View manipulation: To allow users to manipulate the data by filtering conflict types and year, for a high-level or isolated view, to better examine distribution and patterns across time and space. This feature will be incorporated in the time-series analysis using point symbol maps. 

Use of tooltips: Supplementing information about the point event on the point symbol maps when user hovers or clicks on the datapoint. This feature is also incorporated in the stacked area chart (dygraph) whereby frequency values are displayed on the graph upon series/point highlighting.
 zoom and filter
 :
where users can zoom in on a shorter range of dates
Once we spot interesting patterns in the overview, the next logical step is to focus on one in
particular and examine it more closely. 
This method of adjusting the range of time is not only simple to use, but it also
provides the added benefit of keeping us constantly reminded of where the four-week period
that we're currently focusing on fits into the larger 52-week whole

When we explore and try to make sense of data, the Dat visualization help us to follow the
flow of "overview first, zoom and filter, then details-on-demand," bouncing back and forth,
here and there, with ease and without interrupting our train of thought. 


## 2.0 Step-by-step Data Visualisation Preparation
### 2.1 Installing and deploying R packages

tidyverse contains a set of essential packages for data manipulation and exploration.
lubridate
ggplot2
plotly
qicharts2
ggQC
qcc
plyr dplyr dbplyr

```{r code_folding=TRUE}

packages = c('tidyverse','ggplot2','plotly','lubridate','qicharts2','ggQC','qcc','dplyr' )
for(p in packages){
if(!require(p, character.only = T)){
install.packages(p)
}
library(p, character.only = T)
}

```

### 2.2 Data Preparation
#### 2.2.1 Data Source

The data source used in this exercise is from PSA Singapore’s PM anonymised dataset that contains PM operation event records. There are approximately 5 millions records with 69 variables. The dataset is reduced to the following 37 variables for the analysis:

#### 2.2.2 Loading Dataset into R

The Data set is imported using read_csv function which is useful for reading delimited files into data frame.

```{r echo=TRUE, message = TRUE }
ZL_Dataset <- read_csv("data/pm 201903.txt") 
``` 

#### 2.2.3 Exclude unneccessary columns

As the studies focus on PM productivity in yard, we filtered to take in only event_c that are Equipment Mount(EQMT) and Equipment Offload(EQOF) operations. Unused columns are also removed using  subset() function. This reduced the dataset by half to approximately 470MB which is important when dealing with large dataset. 

```{R echo=TRUE}
ZL_DF <- subset(ZL_Dataset, select = -c(3,4,5,10,13,14,16,21,22,23,25,27,28,34,35,36,36,37)) %>%
  filter(EVENT_C %in% c('EQMT','EQOF'))%>%
  filter(SHIFT_D >= 20190328)


```

#### 2.2.4 Convert date columns to date format

It was observed that the variable SHIFT_D and EVENT_DT are in number and char format respectively, as such we convert them using lubridate's function ymd() ymd_hms() and parse them into date-times.   

```{r echo=TRUE}
ZL_DF$SHIFT_D = ymd(as.character(ZL_DF$SHIFT_D))
ZL_DF$EVENT_DT = ymd_hms(as.character(ZL_DF$EVENT_DT))

```


### 3.1 Data Visualisation for Pareto Charts

ggplot
stat_pareto()

using ggplot
#### 3.1.1 summarize data 

We summarize the dataset by the total and average of Wait, Travel, Unproductive and Non-work time, group by the following attributes which will be used as filters for R shiny app. The three millions records now reduced to twelves thousand records which will improve the response time of the pareto charts. A final aggregation for the Pareto chart is done by actual and average time. 

```{r echo=TRUE}

agg_base <-  ZL_DF %>%
  group_by(SHIFT_D,EVENT_SHIFT_I,Terminal,MOVE_OP_C,CNTR_TYPE_C,EQUIPMENT_TYPE_C) %>%
  dplyr::summarise(N=n(),
                   Avg_WAIT_TIME = mean(PM_WAIT_TIME_Q),
                   Total_WAIT_TIME = sum(PM_WAIT_TIME_Q),
                   Avg_TRAVEL_TIME = mean(PM_TRAVEL_TIME_Q), 
                   Total_TRAVEL_TIME = sum(PM_TRAVEL_TIME_Q),
                   Avg_UNPRODUCTIVE_TIME = mean(PM_UNPRODUCTIVE_TIME_Q),
                   Total_UNPRODUCTIVE_TIME = sum(PM_UNPRODUCTIVE_TIME_Q),
                   Avg_NON_WORK_TIME = mean(PM_NON_WORK_TIME_Q),
                   Total_NON_WORK_TIME = sum(PM_NON_WORK_TIME_Q))%>%

  ungroup()
```
```{r echo=TRUE}
agg1 <- agg_base %>%
   dplyr::summarise(Counts = sum(N),
                    Total_WAIT_TIME = sum(Total_WAIT_TIME),
                    Total_TRAVEL_TIME = sum(Total_TRAVEL_TIME),
                    Total_UNPRODUCTIVE_TIME = sum(Total_UNPRODUCTIVE_TIME),
                    Total_NON_WORK_TIME = sum(Total_NON_WORK_TIME),
                    Avg_WAIT_TIME = sum(Total_WAIT_TIME)/sum(N),
                    Avg_TRAVEL_TIME = sum(Total_TRAVEL_TIME)/sum(N),
                    Avg_UNPRODUCTIVE_TIME = sum(Total_UNPRODUCTIVE_TIME)/sum(N),
                    Avg_NON_WORK_TIME = sum(Total_NON_WORK_TIME)/sum(N),
                    
                    Total_Duration = sum(Total_TRAVEL_TIME+Total_WAIT_TIME+Total_UNPRODUCTIVE_TIME+Total_NON_WORK_TIME)
                    )

```

#### 3.1.2 Dataframe and wrap into ggplot.

dataframe 
convert minutes to day unit as the total value is too huge.
plot using ggplot and wrap into plotly for interactively with ggplotly()

(Note: The code for “Average PM operation duration" is similar by using "Avg_" columns and update the labels for title, y & x axis)

```{r echo=TRUE}
Data4Pareto <- data.frame(Time_Indicator = c("Travel Time","Wait Time", "Unproductive Time","Non-Work Time"),
                          Time = c(agg1$Total_TRAVEL_TIME,agg1$Total_WAIT_TIME,
                                   agg1$Total_UNPRODUCTIVE_TIME,
                                   agg1$Total_NON_WORK_TIME),
                          stringsAsFactors = FALSE)
#convert minutes to man-days 
Data4Pareto$Mandays = time_length(dminutes(Data4Pareto$Time), unit = "day")

Data4Pareto <- Data4Pareto[order(Data4Pareto$Mandays,decreasing=TRUE),]
Data4Pareto$Time_Indicator <- factor(Data4Pareto$Time_Indicator, levels=Data4Pareto$Time_Indicator)

```

```{r}
 

p3 <- ggplot(Data4Pareto, aes(x=Time_Indicator, y=Mandays)) +

 stat_pareto(point.size = 3,
             line.color = "black" ) +
  theme_minimal() + 
  labs(title = "Total PM Operation Duration - Pareto Chart", y = "Mandays" , x = "Time spent category"  ) 

ggp3 <- ggplotly(p3)

p3
ggp3
```

```{R}
### average
AvgData4Pareto <- data.frame(Time_Indicator = c("Travel Time","Wait Time", "Unproductive Time","Non-Work Time"),
                             Time = c(agg1$Avg_TRAVEL_TIME,
                                      agg1$Avg_WAIT_TIME,
                                      agg1$Avg_UNPRODUCTIVE_TIME,
                                      agg1$Avg_NON_WORK_TIME))

AvgData4Pareto <- AvgData4Pareto[order(AvgData4Pareto$Time,decreasing=TRUE), ]
AvgData4Pareto$Time_Indicator <- factor(AvgData4Pareto$Time_Indicator,levels=AvgData4Pareto$Time_Indicator)


p4 <- ggplot(AvgData4Pareto, aes(x=Time_Indicator , y=Time)) +
 ggQC::stat_pareto(point.size = 3,
                   line.color = "black") +
  theme_minimal() + 
  labs(title = "Average PM Operation Duration - Pareto Chart", y = "Time (mins)" , x = "Time spent category"  ) 

ggp4 <- ggplotly(p4)

p4
ggp4

```


#### 3.1.3 Paretochart by Qichart2


quick and simple way to plot using paretochart()

applicable to non aggregated dataset.
Also able to wrap into ggplotly. 

```{R echo = TRUE}

# Variable to set Long waiting time definition
longwait <- c(60)

ZL_DF_longwait  <- subset(ZL_DF,ZL_DF$PM_WAIT_TIME_Q >= longwait)


paretochart2 <- paretochart(ZL_DF_longwait$Terminal,xlab = "Terminal",
                            title = paste("PM waiting time >=",longwait ,"mins (Pareto Chart)"),
                            aes(text = paste("Date:", x ,"\n","Avg PM Wait Time:", round(y, 2)) ))
 
 ggparetoTerminal <- ggplotly( paretochart2)
 ggparetoTerminal
# 
# 
# ggparetoMOVE_OP_C <- ggplotly(paretochart(ZL_DF_longwait$MOVE_OP_C,xlab = "Operation Type"))
# ggparetoMOVE_OP_C
# 
# ggparetoLENGTH_Q <- ggplotly(paretochart(ZL_DF_longwait$LENGTH_Q,xlab = "Container Length"))
# ggparetoLENGTH_Q
# 
# ggparetoCNTR_TYPE_C <- ggplotly(paretochart(ZL_DF_longwait$CNTR_TYPE_C,xlab = "Container Type"))
# ggparetoCNTR_TYPE_C
# 
## ggparetoEQUIPMENT_TYPE_C <- ggplotly(paretochart(ZL_DF_longwait$EQUIPMENT_TYPE_C,xlab = "Equipment Type"))
# ggparetoEQUIPMENT_TYPE_C
# # Print data frame

```



### 3.2 Data Visualisation for Control Chart




#### Choice of Packages to render control chart

Three options

ggQC - stat_QC however its QC overlay doesnt work well with plotly.  
Qicharts2
```{r}

qq <- qcc.groups(data = ZL_DF$PM_WAIT_TIME_Q, ZL_DF$SHIFT_D)
q1 = qcc(qq, type = "xbar", nsigmas = 3)

```


```{r}

ZL_DF 
XbarR <- ggplot(ZL_DF, aes(x = SHIFT_D, y = PM_WAIT_TIME_Q)) +
  stat_summary(fun = mean, geom = "point") +
  stat_summary(fun = mean, geom = "line")+

 stat_QC(method = "XmR", auto.label = T,    
          label.digits = 2,    
          show.1n2.sigma = T) 

XbarR
```
```{r}

p1 <- qic(PM_WAIT_TIME_Q,x = SHIFT_D ,data = ZL_DF,chart = 'xbar', ylab = 'Avg WAIT_TIME(Mins)', xlab = 'Date')
p1

```



unfortunately ggQC is fully compatible with Plotly. the reference line and annotation will be dropped

https://www.qimacros.com/free-excel-tips/control-chart-limits/
Is it continuous or discrete?
What is the sample size?
Is the sample size constant?
Each type of data has its own distinct formula for sigma and, therefore, its own type of control chart.

final solution
PICharts to convert to ggplot then wrap to plotly to achieve control chart.  

#### 3.2.1 Xbar chart and S chart with Qicharts2
```{r}

#p1 <- qic(PM_WAIT_TIME_Q,x = SHIFT_D ,data = ZL_DF,chart = 'xbar', ylab = 'Avg WAIT_TIME(Mins)', xlab = 'Date')
p2 <- qic(PM_WAIT_TIME_Q,x = SHIFT_D ,data = ZL_DF,chart = 's', ylab = 'Avg WAIT_TIME(Mins), 2019', xlab = 'Date')

# storing PIcharts into data.frame
df1 <- p1$data
df2 <- p2$data
```

#### load into ggplot
```{r}

ggp1 <- ggplot(df1, aes(x = ymd(x) , y = y , group = 1, text = paste("Date:", x ,"\n","Avg PM Wait Time:", round(y, 2)))) +
  theme_minimal() + 
  geom_line(color = "steelblue", size = 1) +
  geom_point(color = "steelblue", size = 2 ) +
  geom_point(data = subset(df1, y >= ucl), color = "red", size = 2) +
  geom_point(data = subset(df1, y <= lcl), color = "red", size = 2) +
  geom_hline(aes(yintercept = cl),linetype= "dashed") +
  geom_hline(aes(yintercept = aUCL),colour ="red",size = 0.5,linetype= "dashed",summary(p1)) +
  geom_hline(aes(yintercept = aLCL),colour ="red",size = 0.5,linetype= "dashed",summary(p1)) +
  scale_y_continuous(breaks = round(seq(min(df1$y), max(df1$y), by = 0.1),1))+
  #rename tooltip attribute text. 
    labs(title = "Xbar Chart PM Wait Time, 2019" ,
       y = "Avg WAIT_TIME(Mins)", x = "Date")

#ggp1
ggp2 <- ggplot(df2, aes(x = ymd(x) , y = y , group = 1,text = paste("Date:", x ,"\n","Avg PM Wait Time:", round(y, 2)))) +
  theme_minimal() + 
  geom_line(color = "steelblue", size = 1) +
  geom_point(color = "steelblue", size = 2 ) +
  geom_point(data = subset(df2, y >= ucl), color = "red", size = 2) +
  geom_point(data = subset(df2, y <= lcl), color = "red", size = 2) +
  geom_hline(aes(yintercept = cl),linetype= "dashed") +
  geom_hline(aes(yintercept = aUCL),colour ="red",size = 0.5,linetype= "dashed",summary(p2)) +
  geom_hline(aes(yintercept = aLCL),colour ="red",size = 0.5,linetype= "dashed",summary(p2)) +
  scale_y_continuous(breaks = round(seq(min(df2$y), max(df2$y), by = 0.1),1))+
  #rename tooltip attribute text. 
    labs(title = "S Chart PM Wait Time, 2019" ,
       y = "WAIT_TIME (Mins)", x = "Date")

```


#### convert into plotly and add annotations
```{r}
fig1 <- ggplotly(ggp1, tooltip=c("text")) 
  

fig1<- fig1 %>% add_annotations(
    x=17987,
    y=mean(df1$lcl)+0.02,
    xref = "x",
    yref = "y",
    text = paste("LCL=",round(mean(df1$lcl), 2)),
    showarrow = F,
    font = list(color = 'red',size = 10),opacity = 0.5

  )%>% add_annotations(
    x=17987,
    y=mean(df1$ucl+0.02),
    xref = "x",
    yref = "y",
    text = paste("UCL=",round(mean(df1$ucl), 2)),
    showarrow = F,
    font = list(color = 'red',size = 10),opacity = 0.5

  )%>% add_annotations(
    x=17987,
    y=mean(df1$cl)+0.02,
    xref = "x",
    yref = "y",
    text = paste("CL=",round(mean(df1$cl), 2)),
    showarrow = F,
    font = list(color = 'black',size = 10),
   opacity = 0.5

  )


fig1


fig2 <- ggplotly(ggp2, tooltip=c("text")) 
  

fig2<- fig2 %>% add_annotations(
    x=17987,
    y=mean(df2$lcl)+0.02,
    xref = "x",
    yref = "y",
    text = paste("LCL=",round(mean(df2$lcl), 2)),
    showarrow = F,
    font = list(color = 'red',size = 10),opacity = 0.5

  )%>% add_annotations(
    x=17987,
    y=mean(df2$ucl+0.02),
    xref = "x",
    yref = "y",
    text = paste("UCL=",round(mean(df2$ucl), 2)),
    showarrow = F,
    font = list(color = 'red',size = 10),opacity = 0.5

  )%>% add_annotations(
    x=17987,
    y=mean(df2$cl)+0.02,
    xref = "x",
    yref = "y",
    text = paste("CL=",round(mean(df2$cl), 2)),
    showarrow = F,
    font = list(color = 'black',size = 10),
   opacity = 0.5

  )


fig2
```



#### facets

```{r}

p3 <-qic(PM_WAIT_TIME_Q,x = SHIFT_D ,data = ZL_DF,chart = 'xbar', ylab = 'Avg PM_WAIT_TIME', xlab = 'Date',facets   =  EQUIPMENT_TYPE_C ~ EVENT_SHIFT_I)
p4 <-qic(PM_WAIT_TIME_Q,x = SHIFT_D ,data = ZL_DF,chart = 's', ylab = 'Avg PM_WAIT_TIME', xlab = 'Date',facets   =  EQUIPMENT_TYPE_C ~ EVENT_SHIFT_I)

```

```{r}
df3 <- p3$data

ggp3 <- ggplot(df3, aes(x = x , y = y , group = 1, text = paste("Date:", x ,"\n","Avg PM Wait Time:", round(y, 2)))) +
  theme_minimal() + 
  geom_line(color = "steelblue", size = 0.5) +
  geom_point(color = "steelblue", size = 1 ) +
  geom_point(data = subset(df3, y >= ucl), color = "red", size = 1) +
  geom_point(data = subset(df3, y <= lcl), color = "red", size = 1) +
  geom_hline(aes(yintercept = CL),linetype= "dashed",summary(p3)) +
  geom_hline(aes(yintercept = aUCL),colour ="red",size = 0.3,linetype= "dashed",summary(p3)) +
  geom_hline(aes(yintercept = aLCL),colour ="red",size = 0.3,linetype= "dashed",summary(p3)) +
  #scale_y_continuous(df3,breaks = round(seq(min(df3$y), max(df3$y), by = 0.1),1))+
  
  facet_grid(facet1~facet2)+
  #rename tooltip attribute text. 
    labs(title = "Xbar Chart PM Wait Time, 2019" ,
       y = "WAIT_TIME(Mins)", x = "Date")

fig3 <- ggplotly(ggp3, tooltip=c("text"))


fig3


df4 <- p4$data

ggp4 <- ggplot(df4, aes(x = x , y = y , group = 1, text = paste("Date:", x ,"\n","Avg PM Wait Time:", round(y, 2)))) +
  theme_minimal() + 
  geom_line(color = "steelblue", size = 0.5) +
  geom_point(color = "steelblue", size = 1 ) +
  geom_point(data = subset(df4, y >= ucl), color = "red", size = 1) +
  geom_point(data = subset(df4, y <= lcl), color = "red", size = 1) +
  geom_hline(aes(yintercept = CL),linetype= "dashed",summary(p4)) +
  geom_hline(aes(yintercept = aUCL),colour ="red",size = 0.3,linetype= "dashed",summary(p4)) +
  geom_hline(aes(yintercept = aLCL),colour ="red",size = 0.3,linetype= "dashed",summary(p4)) +
  facet_grid(facet1~facet2)+
  #rename tooltip attribute text. 
    labs(title = "S Chart PM Wait Time, 2019" ,
       y = "WAIT_TIME(Mins)", x = "Date")

fig4 <- ggplotly(ggp4, tooltip=c("text"))


fig4
```




#### I(individual) and MR(moving range) chart
```{r}
last_N = 100
 ZL_DF_tail <- tail(ZL_DF, last_N)
# 
P_I <- qic(PM_WAIT_TIME_Q, data = ZL_DF_tail, chart = 'i',  ylab = 'PM_WAIT_TIME', xlab = 'Operations no.' )
P_MR <- qic(PM_WAIT_TIME_Q, data = ZL_DF_tail, chart = 'mr',  ylab = 'PM_WAIT_TIME', xlab = 'Operations no.' )

```


```{r}
DF_I = P_I$data

ggp_I <- ggplot(DF_I, aes(x = x , y = y, text1 = y , text2 = x)  ) +
  theme_minimal() + 
  geom_line(color = "steelblue", size = 1) +
  geom_point(color = "steelblue", size = 2 ) +
  geom_point(data = subset(DF_I, y >= ucl), color = "red", size = 2) +
  geom_point(data = subset(DF_I, y <= lcl), color = "red", size = 2) +
  geom_hline(aes(yintercept = cl),linetype= "dashed") +
  geom_hline(aes(yintercept = aUCL),colour ="red",size = 0.5,linetype= "dashed",summary(P_I)) +
   #scale_y_continuous(breaks = round(seq(min(DF_I$y), max(DF_I$y), by = 10),1))+
   #rename tooltip attribute text. 
    labs(title = "PM Wait Time - I Chart" ,
       y = "WAIT_TIME(Mins)", x = "Operations no.")+
  #if (DF_I$lcl >0) {
   geom_hline(aes(yintercept = aLCL),colour ="red",size = 0.5,linetype= "dashed",summary(P_I)) 
    # }


fig_I <- ggplotly(ggp_I, tooltip=c("text2","text1")) 
  

fig_I<- fig_I %>% add_annotations(
    x=last_N,
    y=mean(DF_I$lcl)+2,
    xref = "x",
    yref = "y",
    text = paste("LCL=",round(mean(DF_I$lcl), 2)),
    showarrow = F,
    font = list(color = 'red',size = 10),opacity = 0.5

  )%>% add_annotations(
    x=last_N,
    y=mean(DF_I$ucl+2),
    xref = "x",
    yref = "y",
    text = paste("UCL=",round(mean(DF_I$ucl), 2)),
    showarrow = F,
    font = list(color = 'red',size = 10),opacity = 0.5

  )%>% add_annotations(
    x=last_N,
    y=mean(DF_I$cl)+2,
    xref = "x",
    yref = "y",
    text = paste("CL=",round(mean(DF_I$cl), 2)),
    showarrow = F,
    font = list(color = 'black',size = 10),
   opacity = 0.5

  )


fig_I

```


```{r}


DF_MR = P_MR$data 

ggp_MR <- ggplot(DF_MR, aes(x = x , y = y, text1 = y , text2 = x)  ) +
  theme_minimal() + 
  geom_line(color = "steelblue", size = 1) +
  geom_point(color = "steelblue", size = 2 ) +
  geom_point(data = subset(DF_MR, y >= ucl), color = "red", size = 2) +
  geom_point(data = subset(DF_MR, y <= lcl), color = "red", size = 2) +
  geom_hline(aes(yintercept = cl),linetype= "dashed") +
  geom_hline(aes(yintercept = aUCL),colour ="red",size = 0.5,linetype= "dashed",summary(P_MR))+
  # scale_y_continuous(breaks = round(seq(min(DF_MR$y), max(DF_MR$y), by = 10),1))+
   #rename tooltip attribute text. 
    labs(title = "PM Wait Time - MR Chart" ,
       y = "WAIT_TIME(Mins)", x = "Operations no.")+
  #if (DF_MR$lcl >=0) {
   geom_hline(aes(yintercept = aLCL),colour ="red",size = 0.5,linetype="dashed",summary(P_MR)) 
   # }


fig_MR <- ggplotly(ggp_MR, tooltip=c("text2","text1")) 
  

fig_MR<- fig_MR %>% add_annotations(
    x=last_N,
    y=mean(DF_MR$lcl)+2,
    xref = "x",
    yref = "y",
    text = paste("LCL=",round(mean(DF_MR$lcl), 2)),
    showarrow = F,
    font = list(color = 'red',size = 10),opacity = 0.5

  )%>% add_annotations(
    x=last_N,
    y=mean(DF_MR$ucl+2),
    xref = "x",
    yref = "y",
    text = paste("UCL=",round(mean(DF_MR$ucl), 2)),
    showarrow = F,
    font = list(color = 'red',size = 10),opacity = 0.5

  )%>% add_annotations(
    x=last_N,
    y=mean(DF_MR$cl)+2,
    xref = "x",
    yref = "y",
    text = paste("CL=",round(mean(DF_MR$cl), 2)),
    showarrow = F,
    font = list(color = 'black',size = 10),
   opacity = 0.5

  )


fig_MR

```

#### C(Count) U(Rate) P(Proportion)

```{r}
 longwait <- c(30)

ZL_DF_longwait  <- subset(ZL_DF,ZL_DF$PM_WAIT_TIME_Q >= longwait)

```
```{R}


agg_Count <-  ZL_DF_longwait %>%
  group_by(SHIFT_D) %>%
  dplyr::summarise(longwait_No =n()
                   )%>%
  ungroup()

 agg_total <-  agg_base %>%
   group_by(SHIFT_D) %>%
   dplyr::summarise(Total_No =sum(N)
                    )%>%
 
   ungroup()

agg_merge <- merge( agg_Count, agg_total, by="SHIFT_D")
 
P_C <- qic(longwait_No,x=SHIFT_D, data = agg_Count, chart = 'c',  ylab = 'Count', xlab = 'Date' )
P_P <- qic(longwait_No,n=Total_No,x=SHIFT_D, data = agg_merge, chart = 'p',   ylab = 'Percent', xlab = 'Date' )
P_U <- qic(longwait_No,n=Total_No,x=SHIFT_D, data = agg_merge, chart = 'u', multiply = 1000,  ylab = 'Count Per 1000 Moves', xlab = 'Date' )

```


```{r}
DF_C = P_C$data

ggp_C <- ggplot(DF_C, aes(x = ymd(x) , y = y, text1 = y , text2 = x)  ) +
  theme_minimal() + 
  geom_line(color = "steelblue", size = 1) +
  geom_point(color = "steelblue", size = 2 ) +
  geom_point(data = subset(DF_C, y >= ucl), color = "red", size = 2) +
  geom_point(data = subset(DF_C, y <= lcl), color = "red", size = 2) +
  geom_hline(aes(yintercept = cl),linetype= "dashed") +
  geom_hline(aes(yintercept = aUCL),colour ="red",size = 0.5,linetype= "dashed",summary(P_C)) +
   #scale_y_continuous(breaks = round(seq(min(DF_C$y), max(DF_C$y), by = 10),1))+
   #rename tooltip attribute text. 
    labs(title = "Long Wait Time - C Chart" ,
       y = "Count", x = "Date")+
  #if (DF_I$lcl >0) {
   geom_hline(aes(yintercept = aLCL),colour ="red",size = 0.5,linetype= "dashed",summary(P_C)) 
    # }


fig_C <- ggplotly(ggp_C, tooltip=c("text2","text1")) 
  

fig_C<- fig_C %>% add_annotations(
    x=17987,
    y=mean(DF_C$lcl)+2,
    xref = "x",
    yref = "y",
    text = paste("LCL=",round(mean(DF_C$lcl), 2)),
    showarrow = F,
    font = list(color = 'red',size = 10),opacity = 0.5

  )%>% add_annotations(
    x=17987,
    y=mean(DF_C$ucl+2),
    xref = "x",
    yref = "y",
    text = paste("UCL=",round(mean(DF_C$ucl), 2)),
    showarrow = F,
    font = list(color = 'red',size = 10),opacity = 0.5

  )%>% add_annotations(
    x=17987,
    y=mean(DF_C$cl)+2,
    xref = "x",
    yref = "y",
    text = paste("CL=",round(mean(DF_C$cl), 2)),
    showarrow = F,
    font = list(color = 'black',size = 10),
   opacity = 0.5

  )


fig_C

```

```{r}
DF_P = P_P$data

ggp_P <- ggplot(DF_P, aes(x = ymd(x) , y = y, text1 = y , text2 = x)  ) +
  theme_minimal() + 
  geom_line(color = "steelblue", size = 1) +
  geom_point(color = "steelblue", size = 2 ) +
  geom_point(data = subset(DF_P, y >= ucl), color = "red", size = 2) +
  geom_point(data = subset(DF_P, y <= lcl), color = "red", size = 2) +
  geom_hline(aes(yintercept = cl),linetype= "dashed") +
  geom_hline(aes(yintercept = aUCL),colour ="red",size = 0.5,linetype= "dashed",summary(P_P)) +
 scale_y_continuous(labels = scales::percent)+
   #scale_y_continuous(breaks = round(seq(min(DF_P$y), max(DF_P$y), by = 10),1))+
   #rename tooltip attribute text. 
    labs(title = "Long Wait Time - P Chart" ,
       y = "Percent", x = "Date")+
  #if (DF_I$lcl >0) {
   geom_hline(aes(yintercept = aLCL),colour ="red",size = 0.5,linetype= "dashed",summary(P_P)) 
    # }


fig_P <- ggplotly(ggp_P, tooltip=c("text2","text1")) 
  

fig_P<- fig_P %>% add_annotations(
    x=17987,
    y=mean(DF_P$lcl+0.0002),
    xref = "x",
    yref = "y",
    text = paste("LCL=",round(mean(DF_P$lcl), 2)),
    showarrow = F,
    font = list(color = 'red',size = 10),opacity = 0.5

  )%>% add_annotations(
    x=17987,
    y=mean(DF_P$ucl+0.0002),
    xref = "x",
    yref = "y",
    text = paste("UCL=",round(mean(DF_P$ucl), 2)),
    showarrow = F,
    font = list(color = 'red',size = 10),opacity = 0.5

  )%>% add_annotations(
    x=17987,
    y=mean(DF_P$cl)+0.0002,
    xref = "x",
    yref = "y",
    text = paste("CL=",round(mean(DF_P$cl), 2)),
    showarrow = F,
    font = list(color = 'black',size = 10),
   opacity = 0.5

  )


fig_P

```

```{r}
DF_U = P_U$data

ggp_U <- ggplot(DF_U, aes(x = ymd(x) , y = y, text1 = y , text2 = x)  ) +
  theme_minimal() + 
  geom_line(color = "steelblue", size = 1) +
  geom_point(color = "steelblue", size = 2 ) +
  geom_point(data = subset(DF_U, y >= ucl), color = "red", size = 2) +
  geom_point(data = subset(DF_U, y <= lcl), color = "red", size = 2) +
  geom_hline(aes(yintercept = cl),linetype= "dashed") +
  geom_hline(aes(yintercept = aUCL),colour ="red",size = 0.5,linetype= "dashed",summary(P_U)) +
   #scale_y_continuous(breaks = round(seq(min(DF_U$y), max(DF_U$y), by = 10),1))+
   #rename tooltip attribute text. 
    labs(title = "Long Wait Time - U Chart" ,
       y = "Count Per 1000 Moves", x = "Date")+
  #if (DF_I$lcl >0) {
   geom_hline(aes(yintercept = aLCL),colour ="red",size = 0.5,linetype= "dashed",summary(P_U)) 
    # }


fig_U <- ggplotly(ggp_U, tooltip=c("text2","text1")) 
  

fig_U<- fig_U %>% add_annotations(
    x=17987,
    y=mean(DF_U$lcl)+0.2,
    xref = "x",
    yref = "y",
    text = paste("LCL=",round(mean(DF_U$lcl), 2)),
    showarrow = F,
    font = list(color = 'red',size = 10),opacity = 0.5

  )%>% add_annotations(
    x=17987,
    y=mean(DF_U$ucl+0.2),
    xref = "x",
    yref = "y",
    text = paste("UCL=",round(mean(DF_U$ucl), 2)),
    showarrow = F,
    font = list(color = 'red',size = 10),opacity = 0.5

  )%>% add_annotations(
    x=17987,
    y=mean(DF_U$cl)+0.2,
    xref = "x",
    yref = "y",
    text = paste("CL=",round(mean(DF_U$cl), 2)),
    showarrow = F,
    font = list(color = 'black',size = 10),
   opacity = 0.5

  )


fig_U
```

### 4.0 Final Data Visualisation

#### limitation 
However, minor to moderate shifts may go unnoticed by the 3-sigma rule for long periods of time.
With fewer data points, they lose sensitivity (more false negatives), and with more data points they lose specificity (more false positives).


### 5.0 Advantages of incorportating interactivity

### 6.0 limitation and future improvement
